Parallax Testing

### 2023-03-30 Fish Data Analysis/Parallax Testing.qmd
Added Charuco Code
Updated paper figures and stats

```{r}
data_2d <- read.csv("Data/Fish_Comp_Values.csv") %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Speed_Diff = abs(Speed_Diff)) %>%
                           mutate(Heading_Diff = abs(Heading_Diff)) %>%
                           mutate(quarter_heading_diff = abs(abs(Heading_Diff-90)-90)) %>%
                           mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
                           mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0))

data_3d_xy <- read.csv("Data/Fish_Comp_Values_3D_xy.csv") %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Speed_Diff = abs(Speed_Diff)) %>%
                           mutate(Heading_Diff = abs(Heading_Diff)) %>%
                           mutate(quarter_heading_diff = abs(abs(Heading_Diff-90)-90)) %>%
                           mutate(Is_Aligned = ifelse(Heading_Diff < 30, 1, 0)) %>%
                           mutate(Is_Reversed = ifelse(Heading_Diff > 150, 1, 0))
```

@@

data_both <- full_join(data_3d_xy_still_sum, data_2d_still_sum) %>% na.omit() %>%
                      mutate(dist_diff = abs(mean_dist_3d_xy - mean_dist_2d))

@@

Graphing NND in 2D
```{r}
ggplot(data_2d_still_sum, aes(round_fish1_x,round_fish1_y, color = mean_dist_2d))+
  geom_point(size = 4, shape = 15)+
  scale_color_viridis() +
  theme_classic() +
  coord_fixed()

@@

>>>>

```{r}
para_vals <- read.csv("Data/Parallax_Distances.csv") %>% mutate(BLs = Distance / 200)

breaks <- c("0.1")

ggplot(para_vals, aes(X, Y, z = BLs))+
  geom_contour_filled(bins = 5, params = c(linewidth = 20))+
  scale_fill_viridis_d("Projection Error (BL)", 
                       labels = c("< 0.1", "0.1 - 0.2", "0.2 - 0.3","0.3 - 0.4","0.4 - 0.5"))+
  theme_classic()+
  coord_fixed() +
  ylab("Vertical Distance from Principal Point (pixels)")+
  xlab("Hoizontal Distance from Principal Point (pixels)")
```

Ignore everything below this, I'm just making a simple graph of predicted values

```{r}
data_2d <- read.csv("Data/Fish_Comp_Values.csv") %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Speed_Diff = abs(Speed_Diff)) %>%
                           mutate(Heading_Diff = abs(Heading_Diff))

data_3d_xy <- read.csv("Data/Fish_Comp_Values_3D_xy.csv") %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Speed_Diff = abs(Speed_Diff)) %>%
                           mutate(Heading_Diff = abs(Heading_Diff))

data_3d <- read.csv("Data/Fish_Comp_Values_3D.csv") %>% mutate(Flow = ifelse(Flow == "0", "Flow 0", "Flow 2")) %>%
                           mutate(Ablation = ifelse(Ablation == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Speed_Diff = abs(Speed_Diff)) %>%
                           mutate(Heading_Diff = abs(Yaw.Heading_Diff))
```

@@

data_both <- full_join(data_3d_xy_still_sum, data_2d_still_sum) %>% na.omit() %>%
                      mutate(dist_diff = mean_dist_3d_xy - mean_dist_2d)

@@

Graphing NND in 2D

```{r}
ggplot(data_2d_still_sum, aes(round_fish1_x,round_fish1_y, color = mean_dist_2d))+
  geom_point(size = 4, shape = 15)+
  scale_color_viridis() +
  theme_classic() +
  coord_fixed()

@@

#Trying a full join for distances

data_2d_merging <- data_2d %>% select(c(Year,Month,Day,Trial,Fish,Tailbeat_Num,Distance,Fish1_X,Fish1_Y,Fish2_X,Fish2_Y))
data_3d_merging <- data_3d_xy %>% select(c(Year,Month,Day,Trial,Fish,Tailbeat_Num,Distance))

data_2d_merging <- data_2d_merging %>% rename(Distance_2D = Distance)
data_3d_merging <- data_3d_merging %>% rename(Distance_3D = Distance)

merged_data <- inner_join(data_2d_merging,data_3d_merging) %>% mutate(Distance_Diff = Distance_2D - Distance_3D) %>% drop_na(Distance_Diff) %>% filter(Distance_Diff < 5)

merged_data <- merged_data %>% mutate(Fish_Mid_X = (Fish1_X + Fish2_X)/2,
                                      Fish_Mid_Y = (Fish1_Y + Fish2_Y)/2)
```

```{r}
ggplot(merged_data, aes(x = Distance_Diff)) +
  geom_histogram()+
  theme_classic()

ggplot(merged_data, aes(x = Fish_Mid_X, y = Fish_Mid_Y, color = Distance_Diff))+
  geom_point()+
  scale_color_viridis() +
  theme_classic()

ggplot(merged_data, aes(x = Fish_Mid_X, y = Fish_Mid_Y, z = Distance_Diff))+
  stat_summary_2d(bins = 20, fun = mean) +
  scale_fill_viridis() +
  theme_classic()

ggplot(merged_data, aes(x = Fish_Mid_X, y = Distance_Diff))+
  geom_point()+
  geom_smooth(se = F, method = "glm", formula = y ~ poly(x,2)) +
  theme_classic()

ggplot(merged_data, aes(x = Fish_Mid_Y, y = Distance_Diff))+
  geom_point()+
  geom_smooth(se = F, method = "glm", formula = y ~ poly(x,2)) +
  theme_classic()
```

```{r}
xy_glm <- glm(Distance_Diff ~ Fish_Mid_X + Fish_Mid_Y, data = merged_data)
x2y_glm <- glm(Distance_Diff ~ I(Fish_Mid_X^2) + Fish_Mid_Y, data = merged_data)
xy2_glm <- glm(Distance_Diff ~ Fish_Mid_X + I(Fish_Mid_Y^2), data = merged_data)
xx2y_glm <- glm(Distance_Diff ~ Fish_Mid_X + I(Fish_Mid_X^2) + Fish_Mid_Y, data = merged_data)
xyy2_glm <- glm(Distance_Diff ~ Fish_Mid_X + Fish_Mid_Y + I(Fish_Mid_Y^2), data = merged_data)
x2y2_glm <- glm(Distance_Diff ~ I(Fish_Mid_X^2) + I(Fish_Mid_Y^2), data = merged_data)

ICtab(xy_glm,x2y_glm,xy2_glm,xx2y_glm,xyy2_glm,x2y2_glm)
```
